A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-13 papers/publication/paper-pollard.tex
Updated R script to generate power plots.
Made a few small changes to the apper. Added the paper pdf.

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{\{spollard,norris\}@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The increasing popularity of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems---one survey in 2014 identified over 80. Since then, the landscape has evolved; some packages have become inactive while more are being developed. Determining the best approach for a given problem is infeasible for most developers. To enable easy, rigorous, and repeatable comparison of the capabilities of such systems, we present an approach and associated software for analyzing the performance and scalability of parallel, open-source graph libraries. We demonstrate our approach on five graph frameworks: GraphMat, the Graph500, the Graph Algorithm Platform, GraphBIG, and PowerGraph using synthetic and real-world datasets. We examine previously overlooked aspects of parallel graph processing performance such as phases of execution and energy usage for three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics.
\end{abstract}

@@

\begin{table}
%	\begin{tabular}{l|r|r|}
%	 & PowerGraph & OpenG \\ \hline
%	BFS & 81.8 & 341 \\ \hline
%	SSSP & 1.64 & 15.0 \\ \hline
%	LCC & 54.6 & 142 \\ \hline
%	\end{tabular}
		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			columns={[index]0,GraphBIG,PowerGraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={dec sep align},
			columns/powergraph/.style={dec sep align}
		]{../report/runtime.csv}
	\caption{Performance results are in milliseconds. LCC is local clustering coefficient, PR is PageRank, CDLP is community detection using label propagation, and WCC is weakly connected components}
	\label{tab:graphalytics}
\end{table}

>>>>

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{spollard@cs.uoregon.edu} \\
	\email{norris@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The increasing popularity of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems---one survey in 2014 identified over 80. Since then, the landscape has evolved; some packages have become inactive while more are being developed. Determining the best approach for a given problem is infeasible for most developers. To enable easy, rigorous, and repeatable comparison of the capabilities of such systems, we present an approach and associated software for analyzing the performance and scalability of parallel, open-source graph libraries. We demonstrate our approach on five graph frameworks: GraphMat, the Graph500, the Graph Algorithm Platform, GraphBIG, and PowerGraph using synthetic and real-world datasets. We examine previously overlooked aspects of parallel graph processing performance such as phases of execution and energy usage for three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics.
\end{abstract}

@@

\begin{table}
	\centering
	\pgfplotstabletypeset[
		col sep=comma,
		columns={[index]0,graphmat,openg,powergraph},
		every head row/.style={after row=\midrule},
		columns/0/.style={string type, column type={l|}, column name={}},
		columns/graphmat/.style={
			column name={GraphMat},
			string replace={0}{},
			dec sep align,
			empty cells with={N/A}
		},
		columns/openg/.style={
		column name={GraphBIG},
			dec sep align},
			columns/powergraph/.style={
			column name={PowerGraph},
			dec sep align}
	]{../report/runtime.csv}
	\caption{Performance results are in milliseconds. LCC is local clustering coefficient, PR is PageRank, CDLP is community detection using label propagation, and WCC is weakly connected components. At the time of this writing, Graphalytics only supports SSSP for GraphMat.}
	\label{tab:graphalytics}
\end{table}
